E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-11 conclusion.tex
chap8 added

\chapter{Conclusion}
We have showcased a novel approach involving black-box testing to identify the presence of E-Mail Header Injection in a web application. Using this approach, we have demonstrated that our system was able to crawl \urls\ web pages finding \forms\ forms, out of which \emailforms\ forms were fuzzable. We fuzzed \fuzzed\ forms and found \recd\  forms that allowed us to send/receive e-mails. Out of these, we were able to inject malicious payloads into \malfuzzed\ forms, identifying \success\ vulnerable forms (\successDelta\ success rate). This indicates that the vulnerability is widespread, and needs attention from both web application developers and library makers.

>>>>

\section{Conclusions}
We have showcased a novel approach involving black-box testing to identify the presence of E-Mail Header Injection in a web application. Using this approach, we have demonstrated that our system was able to crawl \urls\ web pages finding \forms\ forms, out of which \emailforms\ forms were fuzzable. We fuzzed \fuzzed\ forms and found \recd\  forms that allowed us to send/receive e-mails. Out of these, we were able to inject malicious payloads into \malfuzzed\ forms, identifying \success\ vulnerable forms (\successDelta\ success rate). This indicates that the vulnerability is widespread, and needs attention from both web application developers and library makers.

### 2016-05-11 paper.tex
changesto be made
adding chap3
chap4 added
chap5 added
chap6 added
chap7 added
chap8 added

	\section{The {\secit Body} of The Paper}
	Typically, the body of a paper is organized
	into a hierarchical structure, with numbered or unnumbered
	headings for sections, subsections, sub-subsections, and even
	smaller sections.  The command \texttt{{\char'134}section} that
	precedes this paragraph is part of such a
	hierarchy.\footnote{This is the second footnote.  It
		starts a series of three footnotes that add nothing
		informational, but just give an idea of how footnotes work
		and look. It is a wordy one, just so you see
		how a longish one plays out.} \LaTeX\ handles the numbering
	and placement of these headings for you, when you use
	the appropriate heading commands around the titles
	of the headings.  If you want a sub-subsection or
	smaller part to be unnumbered in your output, simply append an
	asterisk to the command name.  Examples of both
	numbered and unnumbered headings will appear throughout the
	balance of this sample document.

	Because the entire article is contained in
	the \textbf{document} environment, you can indicate the
	start of a new paragraph with a blank line in your
	input file; that is why this sentence forms a separate paragraph.

	\subsection{Type Changes and {\subsecit Special} Characters}
	We have already seen several typeface changes in this sample.  You
	can indicate italicized words or phrases in your text with
	the command \texttt{{\char'134}textit}; emboldening with the
	command \texttt{{\char'134}textbf}
	and typewriter-style (for instance, for computer code) with
	\texttt{{\char'134}texttt}.  But remember, you do not
	have to indicate typestyle changes when such changes are
	part of the \textit{structural} elements of your
	article; for instance, the heading of this subsection will
	be in a sans serif\footnote{A third footnote, here.
		Let's make this a rather short one to
		see how it looks.} typeface, but that is handled by the
	document class file. Take care with the use
	of\footnote{A fourth, and last, footnote.}
	the curly braces in typeface changes; they mark
	the beginning and end of
	the text that is to be in the different typeface.

	You can use whatever symbols, accented characters, or
	non-English characters you need anywhere in your document;
	you can find a complete list of what is
	available in the \textit{\LaTeX\
		User's Guide}\cite{Lamport:LaTeX}.

>>>>

	\input{sys_design}

	\input{exp_setup}

	\input{results}

	\input{discussion}

	\input{rel_work}

	\input{conclusion}
